---
title: "TidyTuesdayYarn"
format: html
editor: visual
categories: [analysis, tidytuesday,yarn, interests]
---

This is where I will be putting a short description of analysis 

##Background 
Describe the tidy tuesday prompt and what the user did 
- Code borrowed from https://github.com/awalsh17/ravelry_yarns/blob/main/code/explore_yarn.R
Why am i interested in this?

Add a photo of my projects (in a slide show format)

Code From : https://github.com/isaacarroyov/tidy_tuesday_R/blob/main/scripts_2022/2022_week-41_ravelry-yarn.R
```{r}
library(dplyr)
library(ggplot2)
library(MetBrewer)
library(ggtext)
library(sysfonts)
library(showtext)
```




# ------ LOAD DATA ------
```{r}
yarn <- readr::read_csv('./data/yarn.csv')
```



# ------ DATAVIZ IDEA ------
# Back to hacer algo raro:
# No tengo ni la mas minima idea sobre el tema de yarn, sin embargo es una perfecta 
# oportunidad para hacer una visualizacion poco convencional nada mas por el gusto
# de crear algo.

# ------ DATA WRANGLING ------
df <- yarn %>%
  select(yarn_company_name, rating_average, rating_count,yarn_weight_name) %>%
  tidyr::drop_na()

# ------ (creative) DATA VISUALIZATION ------
df_dataviz <- df %>%
  group_by(yarn_company_name, yarn_weight_name) %>%
  summarise(avg_rating_average = mean(rating_average),
            avg_rating_count = mean(rating_count)) %>%
  ungroup()

# Typography
font_add_google("Vollkorn", "title_font")
font_add_google("Raleway", "body_font")
showtext_auto()

title_font <- "title_font"
body_font <- "body_font"

# Text
title_text <- "Dots and yarn data"
subtitle_text <- "There are no mistakes, only happy accidents.<br>Bob Ross"
caption_text <- "Almost the entire data visualization (the use of points and the colour palette) is inspired by the painting **Notre-Dame-de-la-Garde by Paul Signac** due to the _Pointillist style_.<br>Designed by Isaac Arroyo (@unisaacarroyov on twitter).<br>#TidyTuesday Week 41: Ravelry Yarn via **{ravelRy}**"

# Chart
p1 <- df_dataviz %>%
  ggplot(aes(x = avg_rating_count, y = avg_rating_average, colour = yarn_weight_name)) +
  geom_jitter(width = 0.2, height = 0.1) +
  scale_x_log10(limits =c(1,1e5)) +
  scale_colour_manual(values = met.brewer(name = "Signac", n = 15)) +
  coord_polar() +
  labs(title = title_text, subtitle = subtitle_text, caption = caption_text) +
  theme_void() +
  theme(
    legend.position = "none",
    text = element_text(colour = "gray90"),
    # Title
    plot.title.position = "plot",
    plot.title = element_textbox(family = title_font,
                                 face = 'bold',
                                 lineheight = 0.2,
                                 size = rel(10),
                                 width = unit(8,"in"),
                                 margin = margin(0.125,0,0.125,0,"in"),
                                 hjust = 0.5,
                                 halign = 0.5),
    # Subtitle
    plot.subtitle = element_textbox(family = body_font,
                                    face = 'italic',
                                    lineheight = 0,
                                    size = rel(4),
                                    width = unit(8,"in"),
                                    margin = margin(0,0,-0.5,0,"in"),
                                    hjust = 0.5,
                                    halign = 0.5),
    # Caption
    plot.caption.position = "plot",
    plot.caption = element_textbox(family = body_font,
                                   lineheight = 0.37,
                                   size = rel(2),
                                   width = unit(4,"in"),
                                   margin = margin(-0.5,0,0.125,0,'in'),
                                   hjust = 0.5,
                                   halign = 0.5)
  )
ggsave(filename = "./gallery_2022/2022_week-41_ravelry-yarn.png",
       plot = p1, bg = "#07152A",
       width = 8.5, height = 8.5, units = "in")


```{r}
#| echo: false
#| include: false
#| message: false
#| warning: false
library(tidyverse)
library(caret)
yarnFibers = read_csv("./data/yarn_fibers.csv")
yarn = read_csv("./data/yarn.csv")
```



```{r}
yarn_fibers_wide <- yarnFibers %>%
  distinct(yarn_id, percentage, fiber_type_name) %>%
  group_by(yarn_id) %>%
  mutate(total = sum(percentage)) %>%
  ungroup() %>%
  filter(total == 100) %>%
  distinct(yarn_id, fiber_type_name, .keep_all = TRUE) %>%
  tidyr::pivot_wider(names_from = fiber_type_name, values_from = percentage, values_fill = 0)
```

```{r}
yarn_fibers_top <- yarnFibers %>%
  group_by(yarn_id) %>%
  slice_max(percentage, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  distinct(yarn_id, top_fiber = fiber_type_name)
```

```{r}
yarn_more <- yarn %>%
  left_join(yarn_fibers_top, by = c("id" = "yarn_id"))
```

```{r}
yarn2 <- yarn_more%>%
  mutate(gauge = sapply(strsplit(yarn_weight_knit_gauge, 
                                 split = "-", fixed = TRUE), function(k) mean(as.numeric(k)))) %>%
  mutate(weight_wpi = sapply(strsplit(yarn_weight_wpi, 
                                 split = "-", fixed = TRUE), function(k) mean(as.numeric(k)))) %>%
  separate(texture_clean, into = "texture1", 
           sep = ",", extra = "drop", remove = FALSE) %>%
  mutate(texture_tidy = forcats::fct_lump_n(texture1, 10))
```

```{r}
unique(yarn2$machine_washable)
```


```{r}
yarn3 = yarn2 %>%
  mutate(machine_washable = ifelse(machine_washable %in% c("FALSE", NA), 0, 1)) %>%
  mutate(yarnCompanies = fct_lump(yarn_company_name, 4)) %>%
  select(top_fiber, rating_average, yarnCompanies, yardage) %>%
  drop_na(.)
```

```{r}
yarn_index<- createDataPartition(yarn3$rating_average, p = 0.8, list=FALSE)
yarn_tr <- yarn3[yarn_index,]
yarn_te <- yarn3[-yarn_index,]

control <- trainControl(method ="repeatedcv", number = 5, repeats=3)
m1<- train(rating_average ~ .,
           data = yarn_tr, 
           method = "lm", 
           trControl = control)
print(m1$resample)
```

